---
title: "dsrTest - examples"
author: "Michael Nelson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dsrTest - example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

To demonstrate the functionality of `dsrTest` and the variation in
confidence interval methods, two example datasets are explored below.

The following examples come from Curtin and Klein (1995).

# Simple Hypothetical Example 

All-cause mortality in two similarly sized communities (Curtin and Klein Table A)

```{r Example-1-data}
# community A
A <- data.frame(Age = c('<34', '35-64', '65+'),
                   Deaths = c(20, 120, 360),
                   Population = c(1000, 3000, 6000))
# community B
B <- data.frame(Age = c('<34', '35-64', '65+'),
                   Deaths = c(180, 150, 70),
                   Population = c(6000, 3000, 1000))
# Standard Population 
Standard <- c(3000, 3000, 4000)
```


# Stroke Mortality 

```{r example-2-data}
stroke <- data.frame(
  Deaths = c(1,0,1,2,8,21,46,103,254,371,212),
  Population = c(38,150,322,344,443,379,256,189,136,57,12)*1e3,
  Standard = c(15343,64718,170355,181677,162066,139237,117811,80294,48426,17303,2770))


```

# References

Curtin LR and Klein RJ (1995) 'Direct Standardization (Age-Adjusted Death Rates). Centres for Disease Control and 'Prevention': *Healthy People 2000: Statistical Notes* **6**. https://www.cdc.gov/nchs/data/statnt/statnt06rv.pdf 